---
title: "Week 12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# Same data clean up as last week.

week_12 <- shaming %>% 
  mutate(age = 2006 - birth_year) %>% 
  mutate(treatment = fct_relevel(treatment, "Control")) %>% 
  mutate(solo = ifelse(hh_size == 1, TRUE, FALSE)) %>% 
  select(-general_04, -no_of_names, -birth_year, -hh_size) 
```


## Scene 1

**Prompt:** Create a fitted model object called `fit_1` using this formula or, if you want, a formula which you prefer. You are trying to model `age` as a function of various parameters.

age ~ sex + solo + primary_02 + primary_04 + treatment + sex:solo
                    
```{r}

fit_1 <- stan_glm(data = week_12,
                  age ~ sex + solo + primary_02 + primary_04 + treatment + sex:solo,
                  refresh = 0)
  
fit_1

posterior_interval(prob = .95, fit_1)

```
  
                  
* Is this a causal or predictive model? Why?



* Interpret the fitted model. 



* Should we keep all these variables? And the interaction term?



* Are you surprised about the meaningfulness, or lack thereof, for the treatment variables?




## Scene 2

**Prompt:** Provide a posterior probability distribution for the expected difference in ages between those who live alone and those who do not. (Hint: Given that we are asking for an expected value, use `posterior_epred()`.)

```{r}

new_tibble <- tibble(solo = c(TRUE, FALSE, TRUE, FALSE),
                     sex = c("Female", "Male", "Male", "Female"),
                     primary_02)

posterior_epred(newdata = new_tibble, fit_1)

```






